Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-02-18 WSSSPE2_report/WSSSPE2_review.tex
Front matter: Debug and add myself in comment.
Fix list space.
Fix URL link and volunteer for section 3.
First keynote from live notes.

\usepackage{enumitem}
\setlist{leftmargin=3mm}

@@

\author{TBD by contributions}
%\author{Daniel S. Katz$^{(1)}$, Gabrielle Allen$^{(2)}$, Neil Chue Hong$^{(3)}$, \\
%Karen Cranston$^{(4)}$, Manish Parashar$^{(5)}$, David Proctor$^{(6)}$, \\
%Matthew Turk$^{(2)}$, Colin C. Venters$^{(7)}$, Nancy Wilkins-Diehr$^{(8)}$,}
%Richard Littauer$^{(9)}$ \\
%Miguel de Val-Borro$^{(10)}$
%
%\thanks{{}$^{(1)}$ National Science Foundation, Arlington, VA, USA; Computation Institute, University of Chicago \& Argonne National Laboratory, Chicago, IL, USA}
%
%\thanks{{}$^{(2)}$ University of Illinois, Champaign, IL, USA}
%
%
%\thanks{{}$^{(3)}$ Software Sustainability Institute, University of Edinburgh, Edinburgh, UK}
%  
%\thanks{{}$^{(4)}$ National Evolutionary Synthesis Center, Durham, NC, USA}
%
%\thanks{{}$^{(5)}$ Rutgers Discovery Informatics Institute, Rutgers University, New Brunswick, NJ, USA}
%
%\thanks{{}$^{(6)}$ International Consortium of Research Staff Associations, Dublin, Ireland}
%
%\thanks{{}$^{(7)}$ University of Huddersfield, School of Computing and Engineering, Huddersfield, UK}
%
%\thanks{{}$^{(8)}$ University of California-San Diego, San Diego, CA, USA}
%
%\thanks{{}$^{(9)}$ Saarland University, Saarbr\"{u}cken, Germany}
%
%\thanks{{}$^{(10)}$ Department of Astrophysical Sciences, Princeton University, Princeton, NJ, USA}

@@

\todo{update this section with intro to full report - currently just intro for pre-workshop stuff. Link to live notes -
\url{tinyurl.com/q6ew45v}}
%https://docs.google.com/document/d/1-BxkYWDQ6nNNBXBStUL0xcKF9qCTlEALwf928J_MemI/edit?usp=sharing

@@

The workshop call for papers included the following areas of interest:
\begin{quote}
\begin{itemize}

\item defining software sustainability in the context of science and engineering
software
\begin{itemize}
\item how to evaluate software sustainability
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Keynotes}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\todo{VOLUNTEER NEEDED to write summaries for Kaitlin and Neil's keynotes}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Defining Sustainability}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\todo{writing led by Dan - other contributions welcome}

>>>>

\usepackage{enumitem}
\setlist{leftmargin=7mm}

@@

\author{TBD by contributions}
%\author{Daniel S. Katz$^{(1)}$, Gabrielle Allen$^{(2)}$, Neil Chue Hong$^{(3)}$, \\
%Karen Cranston$^{(4)}$, Manish Parashar$^{(5)}$, David Proctor$^{(6)}$, \\
%Matthew Turk$^{(2)}$, Colin C. Venters$^{(7)}$, Nancy Wilkins-Diehr$^{(8)}$,
%Richard Littauer$^{(9)}$,
%Miguel de Val-Borro$^{(10)}$, 
%Sou-Cheng T. Choi$^{(11)}$}
%
%\thanks{{}$^{(1)}$ National Science Foundation, Arlington, VA, USA; Computation Institute, University of Chicago \& Argonne National Laboratory, Chicago, IL, USA}
%
%\thanks{{}$^{(2)}$ University of Illinois, Champaign, IL, USA}
%
%\thanks{{}$^{(3)}$ Software Sustainability Institute, University of Edinburgh, Edinburgh, UK}
%  
%\thanks{{}$^{(4)}$ National Evolutionary Synthesis Center, Durham, NC, USA}
%
%\thanks{{}$^{(5)}$ Rutgers Discovery Informatics Institute, Rutgers University, New Brunswick, NJ, USA}
%
%\thanks{{}$^{(6)}$ International Consortium of Research Staff Associations, Dublin, Ireland}
%
%\thanks{{}$^{(7)}$ University of Huddersfield, School of Computing and Engineering, Huddersfield, UK}
%
%\thanks{{}$^{(8)}$ University of California-San Diego, San Diego, CA, USA}
%
%\thanks{{}$^{(9)}$ Saarland University, Saarbr\"{u}cken, Germany}
%
%\thanks{{}$^{(10)}$ Department of Astrophysical Sciences, Princeton University, Princeton, NJ, USA}
%
%\thanks{{}$^{(11)}$ NORC at the University of Chicago and   Illinois Institute of Technology, Chicago, IL, USA; \url{sctchoi@uchicago.edu}}

@@

\todo{update this section with intro to full report - currently just intro for pre-workshop stuff. Link to live notes -
\url{http://tinyurl.com/q6ew45v}}
%https://docs.google.com/document/d/1-BxkYWDQ6nNNBXBStUL0xcKF9qCTlEALwf928J_MemI/edit?usp=sharing

@@

The workshop call for papers included the following areas of interest:
\begin{quote}
\begin{itemize} 
\renewcommand{\labelenumi}{\textbf{\theenumi}.}
\setlength{\rightmargin}{1em}
\item defining software sustainability in the context of science and engineering
software
\begin{itemize}
\item how to evaluate software sustainability
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Keynotes}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\todo{Lead: Choi. Volunteers welcome---contact lead.  See \url{http://tinyurl.com/q6ew45v}}
%https://docs.google.com/document/d/1-BxkYWDQ6nNNBXBStUL0xcKF9qCTlEALwf928J_MemI/edit?usp=sharing

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\subsection{Kaitlin Thaney, Designing for Truth, Scale, and Sustainability}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

\begin{enumerate}
\item Why is Mozilla interested in Science: Mozilla is a non-profit interested in openness, in news, in site creation, and in Science, taking advantage of the open web.
\item Current systems designed to create friction --- social issues hindering us
\item case example: National Cancer Institute's caBIG
\begin{itemize}
\item $350m$ spent, $60m+$ for management, $70 + $ tools created, but still seen as a failure (Kaitlin didn't really say why? Were the tools used? Did they immediately bit-rot? Was their development unsustained?). - should ask question about this
\item Those that had the least investment were the most used, the largest investments were the least used.
\item Is there a caBIG report available? Quotes from Andrea Califano/Joe Gray, looks like there is: 
\url{http://tinyurl.com/maf6dz2}%http://www.informationweek.com/architecture/report-blasts-problem-plagued-cancer-research-grid/d/d-id/1097068?
\end{itemize}

\item What do we mean by open research? In regard to community/technology/practices
\item Inefficiency: \url{http://www.xkcd.com/1445/}
\item Need research tools (e.g. software repositories), social capital (e.g. incentives) and capacity (eg training and mentorship) for efficient reproducible research
\item Our systems need to talk to each other but Q for speaker is that as systems become less monolithic, paradoxically it may be harder to sustain the links between them see: 
\begin{itemize}
\item \url{http://tinyurl.com/l76tba2}%http://www.slideshare.net/jameshowison/scientific-software-sustainability-and-ecosystem-complexity
(but does Anon Grizzly have other cites/info for that?)
\item Note, for example, that creative commons licensed works typically don't have dependencies (a book, a photo, an artwork).
\end{itemize}

\item Software Discovery Index: \url{http://softwarediscoveryindex.org/report/}
\item Final points:
\begin{itemize}
\item Design with the audience not the individual in mind
\item Design to unlock latent potential of our systems
\item Rethink how we reward researchers and support roles
\item By mindful of jargon/semantics traps
\end{itemize}
\item Questions:
\begin{itemize}
\item Ted Habermann: if the metadata is minimal less onerous for data provider, but more onerous for user. How to work with data providers to show that users need more.
\item  Find balance between things that have to be captured and what would be ideal. Don't want to get to point where like old Harvard Dataverse, three pages of metadata capture, only first four things ever filled out. Don't want to lose engagement.
\end{itemize}
\end{enumerate}

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\subsection{Neil }
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Defining Sustainability}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\todo{writing led by Dan - other contributions welcome}
